Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

The \code{SkyModel} object represents factorised model that combine the spectral,
spatial and temporal model components (by default the spatial and temporal components are
optional). SkyModel objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.

>>>>

The \code{SkyModel} object represents factorised model that combines the spectral,
spatial and temporal model components (by default the spatial and temporal components are
optional). SkyModel objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.
